---
title: "NCSi-2 Winter 2022/23 COVID-19 vaccination breakthrough: Meta-analysis"
date: "Date compiled: `r format(Sys.time(), '%a %d %B')`"
---

```{r setup, include=FALSE}
source("clear_workspace.r")

knitr::opts_chunk$set(
  cache      = FALSE,
  fig.width  = 8,
  fig.height = 8,
  fig.align  = "center",
  echo       = FALSE,
  message    = FALSE,
  warning    = FALSE
)
```

<style>
.table-hover > tbody > tr:hover { 
  background-color: #fdf7e2;
}
</style>


# Main analysis

- Wales and NI: Suppressed counts between 1 and 9, replaced with a value of 1
- Fully adjusted estimates from all nations
- Combined using fixed-effects meta analysis

### Table: Nation counts and rates

```{r}
t_main_desc_all <- read_xlsx("meta_analysis_results/strict_main_t_desc_all.xlsx")

t_main_desc_all %>% 
kable() %>% 
kable_styling(
  bootstrap   = c("striped", "condensed", "hover"),
  full_width  = FALSE,
  fixed_thead = TRUE
)
```


### Table: Pooled descriptive counts and rates

```{r}
read_xlsx("meta_analysis_results/strxlsx") %>% 
kable(
  align = c("l", "l", "r", "r", "r", "r", "r", "r")
) %>% 
kable_styling(
  bootstrap = c("striped", "condensed", "hover"),
  full_width = FALSE,
  fixed_thead = TRUE
)
```


### Figure: Nation and meta hazard ratios

```{r, fig.height = 15}
qread("meta results/p_main_all_coef.qs")



```

### Figure: Meta hazard ratios

```{r, fig.height = 8}
qread("meta results/p_main_meta_coef.qs")
```

# Specific QCovid conditions

- Wales: Suppressed counts between 1 and 9, replaced with a value of 1
- Model spec includes:
  - Time post vaccination
  - Previous vaccination
  - Demographics: sex, age, household size, area deprivation, urban/rural
  - i.e. not adjusted for other health conditions
- Combined using fixed-effects meta analysis

### Table: Nation counts and rates

```{r}
t_qcovid_desc_all <- read_xlsx("meta results/t_qcovid_descriptive_pool_check.xlsx")

t_qcovid_desc_all %>% 
kable() %>% 
kable_styling(
  bootstrap   = c("striped", "condensed", "hover"),
  full_width  = FALSE,
  fixed_thead = TRUE
) %>% 
column_spec(column =  4, background = ifelse(is.na(t_qcovid_desc_all$n_scotland), "orange", "")) %>% 
column_spec(column =  5, background = ifelse(is.na(t_qcovid_desc_all$n_wales),    "orange", "")) %>% 
column_spec(column =  7, background = ifelse(is.na(t_qcovid_desc_all$e_scotland), "orange", "")) %>% 
column_spec(column =  8, background = ifelse(is.na(t_qcovid_desc_all$e_wales),    "orange", "")) %>%
column_spec(column =  8, background = ifelse(t_qcovid_desc_all$e_wales == 1,      "yellow", ""))
```


### Table: Pooled descriptive counts and rates

```{r}
read_xlsx("meta results/t_qcovid_descriptive_pool_pretty.xlsx") %>% 
select(-xvar) %>% 
kable(
  align = c("l", "r", "r")
) %>% 
kable_styling(
  bootstrap = c("striped", "condensed", "hover"),
  full_width = FALSE,
  fixed_thead = TRUE
)
```

### Figure: Nation and meta hazard ratios

```{r, fig.height = 10}
qread("meta results/p_qcovid_all_coef.qs")
```

### Figure: Meta hazard ratios

```{r, fig.height = 6}
qread("meta results/p_qcovid_meta_coef.qs")
```