---
title  : "Risk of severe COVID-19 outcomers for those who recieved a COVID-19 autumn 2022 vaccination"
date   : "Date compiled: `r format(Sys.time(), '%a %d %B %Y')`"
author : "[Stuart Bedston](mailto:stuart.bedston@swansea.ac.uk)"
---

```{r setup, include=FALSE}

source("r_clear_workspace.r")

options(
	knitr.kable.NA = ''
)

knitr::opts_chunk$set(
	fig.width  = 8,
	fig.height = 8,
	fig.align = "center",
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

```

## 0. Message to SAIL reviewers

The HTML report describes the research aim and study design, lists the data
sources used, the suppression applied to each table and figure, as well as
the context for the other files requested out.

Counts between 1 and 9 are considered "small".

For figures, all small counts have been replaced with 10, and all other counts
rounded to nearest 10.

For descriptive tables, small counts have been omitted, along with their related
stats. All other counts are rounded to nearest 10.


## 1. Research aim

Identify demographic and health characteristics associated with risk of
COVID-19 hospitalisation or death amongst those receiving a COVID-19 vaccination
as part of the autumn 2022 programme.

## 2. Study design

Prospective observational study on a national cohort of those alive and
living in Wales from September 2022, who had received a COVID-19 autumn 2022
vaccination.

Analytical approach is to model time until COVID-19 hosp/death using Cox
regression.

### Data sources

- **C19_COHORT20**:
	- **WDSD**: Welsh Demographic Service Dataset
	- **WLGP**: Welsh Longitudinal General Practice data
- **C19_COHORT_MORTALITY**:
	- **ADDE**: Annual District Death Extract
	- **CDDS**: COVID-19 Consolidated Deaths Data Set
	- **WDSD**: Welsh Demographic Service Dataset
- **(RRDA_)CVVD**: COVID-19 vaccination records from the Welsh Immunisation System
- **PEDW**: Patient Episode Dataset for Wales
- **WDSD**: Welsh Demographic Service Dataset
- **WLGP**: Welsh Longitudinal General Practice data
- **CENW**: ONS census for Wales

## 2. Data extraction / prep

### Figure: Weekly vaccinations by dose num and name

- Counts between 1 and 9 replaced with 10, all other counts rounded to nearest 10

```{r, fig.height = 6}
p_vacc_desc <- qread("results/p_prep_vacc_desc.qs")
p_vacc_desc
```

### Figure: Weekly coverage of current data extract of hospital admissions

- Counts counts rounded to nearest 10

```{r, fig.height = 6}
p_hosp_coverage <- qread("results/p_prep_hosp_coverage.qs")
p_hosp_coverage
```

### Figure: Weekly hospital admissions broken down by COVID-19 status

- Counts between 1 and 9 replaced with 10, all other counts rounded to nearest 10

```{r, fig.height = 12}
p_hosp <- qread("results/p_prep_hosp.qs")
p_hosp
```

## 3. Exploratory analysis

```{r}
qload("results/explore_vacc.qsm")
qload("results/explore_c19_hosp_death.qsm")
```

### Figure: Cumulative incidence of vaccinations

- Suppression not applicable

```{r, fig.height = 7}
p_vacc_state
```

### Figure: COVID-19 combined hosp and death counts per week

- Counts stratified by for those aged 18-64 and 65+, and whether they were up
  up to day 14 post vaccination, if they had recieved an autumn 22 vaccination
- Counts below 10 have been omitted, all other counts rounded to nearest 10

```{r, fig.height = 6}
p_c19_hosp_death_week
```

### Table: Total COVID-19 hosp/death counts by age

- Counts between 1 and 9 have been removed, all other counts rounded to nearest 10

```{r}
bind_rows(t_c19_hosp_death_n, .id = "outcome") %>%
mutate(across(where(is.numeric), suppress_n)) %>%
kable(
	align = c("l", "r", "r"),
	format.args = list(big.mark = ",")
) %>%
kable_pretty()
```

## 4. Sample selection

### Table: Sample selection

- Counts rounded to nearest 10

```{r}
qread("results/t_sample_selection.qs") %>%
mutate(
	n = suppress_n(n),
	n_diff = suppress_n(n_diff)
) %>%
kable(
	align = c("r", "l", "r", "r", "r"),
	format.args = list(big.mark = ",")
) %>%
kable_pretty()
```

## 5. Main analysis of severe COVID-19 outcomes

```{r}
qload("results/analyse_hosp_death_main.qsm")
```

### Table: Sample descriptives, counts and rates of severe COVID-19 outcome

- Counts between 1 and 9, excluded, along with derived columns, such as percentage or rate
- All other counts rounded to nearest 10
- Percentages and rates are reported to 1 decimal place
- The table below is also saved as:
	+ `t_hosp_death_overall_npr.csv`
- Also suppressed and saved are the sample descriptives for the MD and PB specific subsets:
	+ `t_hosp_death_md_npr.csv`
	+ `t_hosp_death_pb_npr.csv`

```{r}

t_hosp_death_overall_npr <-
	hosp_death_overall_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

t_hosp_death_overall_npr %>%
kable(
	format.args = list(big.mark = ",")
) %>%
kable_pretty()

write_csv(
	t_hosp_death_overall_npr,
	file = "request-out/t_hosp_death_overall_npr.csv"
)

# output the two MD and PB subsets

t_hosp_death_md_npr <-
	hosp_death_md_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

write_csv(
	t_hosp_death_md_npr,
	file = "request-out/t_hosp_death_md_npr.csv"
)

t_hosp_death_pb_npr <-
	hosp_death_pb_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

write_csv(
	t_hosp_death_pb_npr,
	file = "request-out/t_hosp_death_pb_npr.csv"
)

```


### Figure: Hazard ratios of severe COVID-19 outcome

- Suppression not applicable
- Adjusted coef for overall, MD-and PB-specific analyses are saved as:
	+ `m_hosp_death_overall_coef_adj.csv`
	+ `m_hosp_death_md_coef_adj.csv`
	+ `m_hosp_death_pb_coef_adj.csv`
- Respective variance-covariance matrices are saved as:
	+ `m_hosp_death_overall_vcov_adj.csv`
	+ `m_hosp_death_md_vcov_adj.csv`
	+ `m_hosp_death_pb_vcov_adj.csv`


```{r, fig.height = 10}
p_hosp_death_coef

# coefs
write_csv(hosp_death_overall_coef_adj, file = "request-out/m_hosp_death_overall_coef_adj.csv")
write_csv(hosp_death_md_coef_adj,      file = "request-out/m_hosp_death_md_coef_adj.csv")
write_csv(hosp_death_pb_coef_adj,      file = "request-out/m_hosp_death_pb_coef_adj.csv")

# variance-covariance
hosp_death_overall_vcov_adj %>%
as_tibble() %>%
write_csv(file = "request-out/m_hosp_death_overall_vcov_adj.csv")

hosp_death_md_vcov_adj %>%
as_tibble() %>%
write_csv(file = "request-out/m_hosp_death_md_vcov_adj.csv")

hosp_death_pb_vcov_adj %>%
as_tibble() %>%
write_csv(file = "request-out/m_hosp_death_pb_vcov_adj.csv")
```

## 6. Analysis of severe COVID-19 outcomes for QCovid clinical indicators

```{r}
qload("results/analyse_hosp_death_qcovid.qsm")
```

### Table: Sample counts and rates of severe COVID-19 outcome

- Counts between 1 and 9 have been excluded, along with derived columns, such as percentage and rate
- All other counts rounded to nearest 10
- Percentages and rates are reported to 1 decimal place
- Saved as `t_hosp_death_qcovid_npr.csv`

```{r}
t_hosp_death_qcovid_npr <-
	hosp_death_qcovid_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = if_else(is.na(total_n), NA_real_, round_half_up(pyears, 1)),
		events  = if_else(is.na(total_n), NA_real_, suppress_n(events)),
		rate    = if_else(is.na(events),  NA_real_, round_half_up(rate, 1))
	)

t_hosp_death_qcovid_npr %>%
kable(
	format.args = list(big.mark = ",")
) %>%
kable_pretty()

write_csv(
	t_hosp_death_qcovid_npr,
	file = "request-out/t_hosp_death_qcovid_npr.csv"
)
```

### Figure: Hazard ratios of severe COVID-19 outcome

- Results suppressed for covariates with a prevalence count of less than 10
  (total N from the previous table)
- Saved as `m_hosp_death_qcovid_coef_adj.csv`

```{r, fig.height = 10}
p_hosp_death_qcovid_coef

d_hosp_death_qcovid_coef %>%
filter(est_type == "adj") %>%
select(-est_type) %>%
write_csv(
	file = "request-out/m_hosp_death_qcovid_coef_adj.csv"
)
```
