---
title  : "Risk of severe COVID-19 outcomers for those who recieved a COVID-19 autumn 2022 vaccination"
date   : "Date compiled: `r format(Sys.time(), '%a %d %B %Y')`"
author : "[Stuart Bedston](mailto:stuart.bedston@swansea.ac.uk)"
---

```{r setup, include=FALSE}

source("r_clear_workspace.r")

options(
	knitr.kable.NA = ''
)

knitr::opts_chunk$set(
	fig.width  = 8,
	fig.height = 8,
	fig.align = "center",
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

```

## . Sample selection

### Table: Sample selection

- Counts rounded to nearest 10

```{r}
qread("../results/t_sample_selection.qs") %>%
mutate(
	n = suppress_n(n),
	n_diff = suppress_n(n_diff)
) %>%
kable(
	align = c("r", "l", "r", "r", "r"),
	format.args = list(big.mark = ",")
) %>%
kable_pretty()
```

## 2. Main analysis of severe COVID-19 outcomes

```{r}
qload("../results/analyse_hosp_death_main.qsm")
```

### Table: Sample descriptives, counts and rates of severe COVID-19 outcome

- Counts between 1 and 9, excluded, along with derived columns, such as percentage or rate
- All other counts rounded to nearest 10
- Percentages and rates are reported to 1 decimal place
- The table below is also saved as:
	+ `t_hosp_death_overall_npr.csv`
- Also suppressed and saved are the sample descriptives for the MD and PB specific subsets:
	+ `t_hosp_death_md_npr.csv`
	+ `t_hosp_death_pb_npr.csv`

```{r}

t_hosp_death_overall_npr <-
	hosp_death_overall_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

t_hosp_death_overall_npr %>%
kable(
	format.args = list(big.mark = ",")
) %>%
kable_pretty()

write_csv(
	t_hosp_death_overall_npr,
	file = "../results/t_hosp_death_overall_npr.csv"
)

# output the two MD and PB subsets

t_hosp_death_md_npr <-
	hosp_death_md_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

write_csv(
	t_hosp_death_md_npr,
	file = "../results/t_hosp_death_md_npr.csv"
)

t_hosp_death_pb_npr <-
	hosp_death_pb_npr %>%
	mutate(
		total_n = suppress_n(total_n),
		total_p = if_else(is.na(total_n), NA_real_, round_half_up(total_p, 1)),
		pyears  = suppress_n(pyears),
		events  = suppress_n(events),
		rate    = if_else(is.na(events), NA_real_, round_half_up(rate, 1))
	)

write_csv(
	t_hosp_death_pb_npr,
	file = "../results/t_hosp_death_pb_npr.csv"
)

```


### Figure: Hazard ratios of severe COVID-19 outcome

- Suppression not applicable
- Adjusted coef for overall, MD-and PB-specific analyses are saved as:
	+ `m_hosp_death_overall_coef_adj.csv`
	+ `m_hosp_death_md_coef_adj.csv`
	+ `m_hosp_death_pb_coef_adj.csv`
- Respective variance-covariance matrices are saved as:
	+ `m_hosp_death_overall_vcov_adj.csv`
	+ `m_hosp_death_md_vcov_adj.csv`
	+ `m_hosp_death_pb_vcov_adj.csv`


```{r, fig.height = 10}
p_hosp_death_coef

# coefs
write_csv(hosp_death_overall_coef_adj, file = "../results/m_hosp_death_overall_coef_adj.csv")
write_csv(hosp_death_md_coef_adj,      file = "../results/m_hosp_death_md_coef_adj.csv")
write_csv(hosp_death_pb_coef_adj,      file = "../results/m_hosp_death_pb_coef_adj.csv")

# variance-covariance
hosp_death_overall_vcov_adj %>%
as_tibble() %>%
write_csv(file = "../results/m_hosp_death_overall_vcov_adj.csv")

hosp_death_md_vcov_adj %>%
as_tibble() %>%
write_csv(file = "../results/m_hosp_death_md_vcov_adj.csv")

hosp_death_pb_vcov_adj %>%
as_tibble() %>%
write_csv(file = "../results/m_hosp_death_pb_vcov_adj.csv")
```
